Considering scale in multilayer animal social networks

### 2020-06-11 paper/manuscript.Rmd
soc scale

We modified the spatial distance threshold used for
group assignment using `spatsoc` [@Robitaille_2019] and re-assigned groups at
incremental distances between 5 and 500 m (5, 25, 50, 75, 100, 250, 500). For example, at the finest
scale, only individuals within 5 m of one another were considered in the same
group, whereas at the coarsest scale, individuals within 500 m of one
another were considered in the same group. We assumed these scales represented
visual (short distance) to auditory (long distance) sensory modalities of
caribou. <!-- TODO: clarify not attempting ML with multiple behaviours -->

@@

To assess the influence of spatial scale on multilayer networks, we aggregated
our land cover raster at varying scales relevant to caribou ecology. We
aggregated the 30 m land cover raster using the R package `grainchanger`
[@Graham_2019] at five scales: 100 m, 250 m, 500 m, 750 m and 1000 m. Aggregation
occurred using a modal moving window method using a circular window
corresponding to the above scales [@Graham_2019a]. We assume 30 m and 100 m
represents fine-scale decision making for caribou during foraging, while
re-sampling at 500 m , 750 m and 1000 m represents the scale at which caribou tend to
select and avoid habitat (Bastille-Rousseau et al. 2017).

>>>>

We generated multilayer networks across a series of spatial distance thresholds
for group assignment. Spatial distance thresholds (5, 25, 50, 75, 100, 250 and
500 m) represented a range of visual (short distance) to auditory (long
distance) sensory modalities of caribou. Multilayer networks consisted of the
social association between `r DT[, uniqueN(get(idcol))]` individuals across
three habitat layers (open, forest and forage). At the finest scale, individuals
within 5 m of one another were considered in the same group, whereas at the
coarsest scale, individuals within 500 m of one another were considered in the
same group. We calculated graph strength and multidegree for each habitat layer
and spatial distance threshold, and edge overlap across the entire series of
networks to determine proportion of total edges observed in each combination of
habitat layer and spatial distance threshold.

@@

To assess the influence of spatial scale on multilayer networks, we aggregated
our land cover raster at varying scales <!--relevant to caribou ecology. We
aggregated the 30 m land cover raster using the R package `grainchanger`
[@Graham_2019] at five scales: 100 m, 250 m, 500 m, 750 m and 1000 m. Aggregation
occurred using a modal moving window method using a circular window
corresponding to the above scales [@Graham_2019a]. We assume 30 m and 100 m
represents fine-scale decision making for caribou during foraging, while
re-sampling at 500 m , 750 m and 1000 m represents the scale at which caribou tend to
select and avoid habitat (Bastille-Rousseau et al. 2017).
